%-------------------------
% US Resume - DevOps / Cloud Engineer
% Bullet: • (100% consistent)
% Spacing: US resume standard (readable, not cramped)
%-------------------------

\documentclass[letterpaper,11pt]{article}

% ---------------- PACKAGES ----------------
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\input{glyphtounicode}

% ---------------- PAGE STYLE ----------------
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% ---------------- MARGINS (US STANDARD) ----------------
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.6in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% ---------------- SECTION FORMAT ----------------
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

\pdfgentounicode=1

% ---------------- CUSTOM COMMANDS ----------------
\newcommand{\resumeItem}[1]{
  \item \small{#1}
}

\newcommand{\resumeItemListStart}{
  \begin{itemize}[leftmargin=*, itemsep=4pt, topsep=0pt, label=\textbullet]
}
\newcommand{\resumeItemListEnd}{
  \end{itemize}\vspace{4pt}
}

\newcommand{\resumeSubHeadingListStart}{
  \begin{itemize}[leftmargin=0in, label={}]
}
\newcommand{\resumeSubHeadingListEnd}{
  \end{itemize}
}

\newcommand{\resumeSubheading}[4]{
  \item
    \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{3pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
    \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
    \end{tabular*}\vspace{1pt}
}

% ---------------- DOCUMENT ----------------
\begin{document}
\setlist[itemize]{label=\textbullet}

% ---------------- HEADER ----------------
\begin{center}
  {\Huge \scshape Pham Duy Chien} \\[6pt]
  {\Large Fresher Cloud / DevOps Engineer} \\[8pt]
  \faPhone\ +84 833 998 180 \quad
  \href{mailto:phamchien152003@gmail.com}{\faEnvelope\ phamchien152003@gmail.com} \quad
  \href{https://www.linkedin.com/in/chienpham-software-engineer}{\faLinkedin\ LinkedIn} \quad
  \href{https://github.com/benphamse}{\faGithub\ GitHub}
\end{center}

% ---------------- SUMMARY ----------------
\section{Summary}
Cloud/DevOps Engineer with hands-on experience in Infrastructure as Code, CI/CD automation, and cloud-native systems.
Strong foundation in AWS, Terraform, Docker, Kubernetes, and backend systems. Aspires to grow into a
Data-Driven DevOps \& AIOps Architect building scalable, secure, and automated platforms.

% ---------------- EDUCATION ----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
  {Ho Chi Minh City University of Technology and Education}{2022 -- 2026 (Expected)}
  {B.Sc. in Information Security Engineering}{GPA: 3.55 / 4.0}
\resumeSubHeadingListEnd

% ---------------- SKILLS ----------------
\section{Skills}
\textbf{Languages:} Python, Java, C++, JavaScript, Shell \\
\textbf{Frameworks:} Spring Boot, Express.js \\
\textbf{Databases:} PostgreSQL, MySQL, SQL Server, Redis, Elasticsearch \\
\textbf{Cloud \& Containers:} AWS, OpenStack, Docker, Kubernetes \\
\textbf{CI/CD \& IaC:} GitHub Actions, Azure DevOps, GitLab CI, Terraform \\
\textbf{Monitoring \& Logging:} Prometheus, Zabbix, Kibana, Fluentd, Vector \\
\textbf{Security \& Testing:} SAST (Snyk), Trivy, Arachni, Performance Testing (k6)

% ---------------- EXPERIENCE ----------------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
  {DevOps / Cloud Engineer (Intern $\rightarrow$ Fresher)}{Jul 2025 -- Present}
  {Emesoft JSC}{}
\resumeItemListStart
  \resumeItem{Maintained and enhanced Terraform modules to standardize cloud resource provisioning across environments.}
  \resumeItem{Designed and implemented CI/CD pipelines using GitHub Actions and Azure DevOps for application and data projects.}
  \resumeItem{Automated infrastructure and deployment workflows while integrating security checks into pipelines.}
  \resumeItem{Promoted from Intern to Fresher based on performance, learning speed, and delivery quality.}
\resumeItemListEnd

\resumeSubheading
  {System Engineer Intern}{Feb 2025 -- Jun 2025}
  {AES Company}{}
\resumeItemListStart
  \resumeItem{Configured and managed routers, switches, and servers to ensure high availability and stable performance.}
  \resumeItem{Collaborated with IoT teams to deploy network infrastructure optimized for IoT environments.}
  \resumeItem{Built strong fundamentals in networking, infrastructure operations, and cross-team collaboration.}
\resumeItemListEnd

\resumeSubHeadingListEnd

% ---------------- PROJECTS ----------------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
  {Digitraker $|$ DevOps / Cloud Engineer}{Sep 2025 -- Nov 2025}
\resumeItemListStart
  \resumeItem{Designed reusable Terraform modules to provision AWS infrastructure including VPC, EC2, subnets, and security groups.}
  \resumeItem{Implemented multi-environment setups (dev/staging/prod) using parameterized variables and remote state management.}
  \resumeItem{Integrated Infrastructure as Code workflows into CI/CD pipelines for automated provisioning and updates.}
  \resumeItem{Applied security-by-design practices including least-privilege IAM and encrypted resources.}
  \resumeItem{\textbf{Tech stack:} Terraform, AWS, Azure DevOps}
\resumeItemListEnd
\resumeProjectHeading
  {Civic+ $|$ DevOps / Cloud Engineer}{Aug 2025 -- Present}
\resumeItemListStart
  \resumeItem{Provisioned and maintained cloud infrastructure for Document Service using Infrastructure as Code.}
  \resumeItem{Automated CI/CD pipelines to deploy infrastructure changes reliably across environments.}
  \resumeItem{\textbf{Tech stack:} Terraform, AWS, Azure DevOps}
\resumeItemListEnd
\resumeProjectHeading
  {Project Harmony (PracticeTek) $|$ DevOps / Cloud Engineer}{Aug 2025 -- Present}
\resumeItemListStart
  \resumeItem{Contributed to data migration pipelines centralizing business data into Zuora.}
  \resumeItem{Maintained Infrastructure as Code supporting Dev, QA, and Production environments.}
  \resumeItem{Worked within a monorepo containing applications, data pipelines, and shared DevOps tooling.}
  \resumeItem{\textbf{Tech stack:} Terraform, AWS, GitHub Actions}
\resumeItemListEnd
\resumeProjectHeading
  {Tea Shop $|$ Backend Developer}{Oct 2024 -- Dec 2024}
\resumeItemListStart
  \resumeItem{Developed backend services using Spring Boot following layered architecture principles.}
  \resumeItem{Implemented authentication and authorization using Spring Security.}
  \resumeItem{Integrated VNPay for secure payment processing and managed MySQL database.}
  \resumeItem{\textbf{GitHub:} \href{https://github.com/AiNga04/Ecommerce}{github.com/AiNga04/Ecommerce}}
  \resumeItem{\textbf{Tech stack:} Spring Boot, MySQL, JSP}
\resumeItemListEnd
\resumeProjectHeading
  {Banking App $|$ Backend Developer}{Apr 2024 -- Jul 2024}
\resumeItemListStart
  \resumeItem{Developed a banking application using Java and Spring Boot supporting both admin and end-user roles.}
  \resumeItem{Integrated Firebase Realtime Database to deliver real-time notifications for transactions and user events.}
  \resumeItem{Collaborated with Android developers to deliver an end-to-end banking solution across backend and mobile platforms.}
  \resumeItem{\textbf{Backend GitHub:} \href{https://github.com/benphamse/BankingApp}{github.com/benphamse/BankingApp}}
  \resumeItem{\textbf{Mobile GitHub:} \href{https://github.com/benphamse/Android-App-Banking}{github.com/benphamse/Android-App-Banking}}
  \resumeItem{\textbf{Tech stack:} Spring Boot, MySQL, Firebase, Android, SQLite}
\resumeItemListEnd
\resumeSubHeadingListEnd

% ---------------- CERTIFICATIONS ----------------
\section{Certifications \& Honors}
\resumeItemListStart
  \resumeItem{\textbf{AWS Certified CloudOps Engineer – Associate} (Jan 2026 -- Jan 2029)}
  \resumeItem{\textbf{TOEIC 870} (Nov 2024 -- Nov 2026)}
  \resumeItem{Academic Scholarship – Academic Year 2024--2025}
  \resumeItem{Participant, CTF HCMUTE 2024 (Cybersecurity Competition)}
  \resumeItem{Participant, Mastering IT 2024 (Academic IT Competition)}
\resumeItemListEnd

\end{document}