\documentclass[11pt,a4paper,sans]{article}

% % ===== ENCODING & LANGUAGE =====
\usepackage{fontspec}
\setmainfont{Times New Roman}
\usepackage[vietnamese]{babel}

% --- Packages ---
\usepackage[utf8]{inputenc}
\usepackage[vietnamese]{babel}
\usepackage[left=1.25cm, right=1.25cm, top=1.25cm, bottom=1.25cm]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage{tabularx}
\usepackage{array}

% --- UI config ---
\pagestyle{empty}
\hypersetup{colorlinks=true, urlcolor=blue}

% Section format
\titleformat{\section}{\large\bfseries\uppercase}{}{0pt}{}[\titlerule]
\titlespacing{\section}{0pt}{12pt}{8pt}

% List spacing
\setlist[itemize]{leftmargin=1.5em, nosep, topsep=2pt, itemsep=2pt}

% --- Entry macro ---
\newcommand{\entryheader}[4]{
    \noindent \textbf{#1} \hfill #2 \\
    \noindent \textit{#3} \hfill \textit{#4} \par
    \vspace{2pt}
}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\Huge \textbf{PHẠM DUY CHIẾN}} \\[4pt]
    {\large Fresher Cloud / DevOps Engineer} \\[8pt]

    \small
    \faPhone\ 0833998180 \quad
    \faEnvelope\ \href{mailto:phamchien152003@gmail.com}{phamchien152003@gmail.com} \quad
    \faMapMarker*\ TP Hồ Chí Minh, Việt Nam \\[4pt]

    \faGithub\ \href{https://github.com/benphamse}{benphamse} \quad
    \faLinkedin\ \href{https://www.linkedin.com/in/chienpham-software-engineer}{chienpham-software-engineer}
\end{center}


% ===== OBJECTIVE =====
\section{Objective}
\noindent
As a dedicated and detail-oriented Cloud \& DevOps Engineer with a strong foundation in
Cloud Infrastructure, Data Engineering, and Automation, I aim to become a
\textbf{Data-Driven DevOps \& AI Architect} within the next 3--5 years.
My passion lies in building scalable, secure, and data-centric systems, designing
AI/ML-enabled pipelines, and applying AIOps practices to enhance system reliability,
observability, and business intelligence.

% ===== EDUCATION =====
\section{Education}
\entryheader{Ho Chi Minh City University of Technology and Education}
{2022 -- Expected 2026}
{Bachelor’s Degree in Information Security Engineering}
{CPA: 3.55 / 4.0}

% ===== SKILLS =====
\section{Skills}
\noindent
\begin{minipage}[t]{0.5\textwidth}
\begin{tabular}{@{}p{3cm} p{5.5cm}@{}}
\textbf{Languages:} & C++, Java, Python, JavaScript, Shell \\
\textbf{Frameworks:} & Spring Boot, Express.js \\
\textbf{Databases:} & MySQL, PostgreSQL, SQL Server, Redis \\
\textbf{Cloud:} & AWS, OpenStack \\
\textbf{Containers:} & Docker, Kubernetes \\
\end{tabular}
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
\begin{tabular}{@{}p{3cm} p{5.5cm}@{}}
\textbf{CI/CD:} & GitHub Actions, Azure Pipelines, GitLab CI \\
\textbf{IaC:} & Terraform \\
\textbf{Monitoring:} & Prometheus, Zabbix \\
\textbf{Logging:} & Elasticsearch, Kibana, Fluentd, Vector \\
\textbf{Testing:} & K6, Snyk (SAST), Trivy, Arachni \\
\end{tabular}
\end{minipage}

% ===== EXPERIENCE =====
\section{Work Experience}

\entryheader{Emesoft JSC}
{Jul 2025 -- Present}
{DevOps / Cloud Engineer Intern / Fresher}
{}
\begin{itemize}
\item Maintained and enhanced Terraform modules to standardize cloud resource provisioning.
\item Designed and implemented CI/CD pipelines for Data and Application projects using GitHub Actions and Azure Pipelines.
\item Automated deployment workflows and integrated security checks into pipelines.
\item \textbf{Achievement:} Successfully promoted from Intern to Fresher through strong technical delivery.
\end{itemize}

\vspace{6pt}
\entryheader{AES Company}
{Feb 2025 -- Jun 2025}
{System Engineer Intern}
{}
\begin{itemize}
\item Configured and managed routers, switches, and servers to ensure high availability.
\item Collaborated with IoT teams to design and deploy network infrastructure for IoT systems.
\item Built strong foundation in networking protocols and system operations.
\end{itemize}

% ===== PROJECTS =====
\section{Projects}

\entryheader{Civic+}
{Aug 2025 -- Present}
{DevOps / Cloud Engineer}
{Team size: 30}
\begin{itemize}
\item Designed and implemented IaC for provisioning infrastructure for Document Service.
\item Integrated Terraform workflows into CI/CD pipelines for automated infrastructure updates.
\item Supported multi-environment deployments to ensure scalability and stability.
\item \textbf{Tech stack:} Terraform, AWS, Azure Pipelines.
\end{itemize}

\vspace{6pt}
\entryheader{Project Harmony (PracticeTek)}
{Aug 2025 -- Present}
{DevOps / Cloud Engineer}
{Team size: 11}
\begin{itemize}
\item Contributed to data migration pipelines to centralize business data into Zuora.
\item Managed monorepo structure including frontend, data pipelines, and shared tooling.
\item Implemented IaC to provision AWS resources and supported SDLC across Dev/QA/Prod.
\item \textbf{Tech stack:} Terraform, AWS, GitHub Actions.
\end{itemize}

\vspace{6pt}
\entryheader{Project Digitraker}
{Sep 2025 -- Nov 2025}
{DevOps / Cloud Engineer}
{Team size: 8}
\begin{itemize}
\item Designed and implemented Terraform scripts to provision cloud infrastructure.
\item Integrated IaC with CI/CD pipelines for automated deployments.
\item Applied security best practices including IAM roles and security groups.
\item \textbf{Tech stack:} Terraform, AWS, Azure Pipelines.
\end{itemize}

\vspace{6pt}
\entryheader{Tea Shop}
{Oct 2024 -- Dec 2024}
{Backend Developer}
{Team size: 2}
\begin{itemize}
\item Developed backend services using Spring Boot.
\item Implemented authentication and authorization with Spring Security.
\item Integrated VNPay for secure payment processing.
\item \textbf{Tech stack:} Spring Boot, MySQL, JSP.
\end{itemize}

\vspace{6pt}
\entryheader{Banking App}
{Apr 2024 -- Jul 2024}
{Backend Developer}
{Team size: 4}
\begin{itemize}
\item Developed banking features for admin and user roles using Spring Boot.
\item Designed secure database schema and managed deployment processes.
\item Integrated Firebase Realtime Database for transaction notifications.
\item \textbf{Tech stack:} Spring Boot, Android, MySQL, Firebase, SQLite.
\end{itemize}

% ===== CERTIFICATIONS =====
\section{Certifications \& Honors}
\noindent \textbf{AWS Certified CloudOps Engineer – Associate} \hfill \textit{Jan 2026 -- Jan 2029} \\
\noindent \textbf{TOEIC 870} – Proficient in English reading and writing. \hfill \textit{Nov 2024 -- Nov 2026} \\
\noindent \textbf{Academic Scholarship} – Top academic performance. \hfill \textit{2024--2025} \\
\noindent \textbf{CTF HCMUTE \& Mastering IT} – Cybersecurity and IT competitions. \hfill \textit{2024}

\end{document}